### 2014-02-22 thesis/src/chapters/chapter-implementation.tex
Thesis: added stack manager

\subsubsection{Objectives}
What lies in duties of a stack manager is:
\begin{itemize}
 \item supervising and scaling out stack
 \item delegating problem to a cloud instance manager, when not capable of resolving it
\end{itemize}

@@

@@

% darek
\subsection{Cloud provider client}

% darek
\section{Cloud provider}

>>>>

\subsubsection{Objectives}
What lies in duties of a stack manager is:
\begin{itemize}
\item deploying stack
 \item supervising and scaling out stack
 \item delegating problem to a cloud instance manager, when not capable of resolving it
\end{itemize}

@@

\begin{asparaenum}
 \item[\textbf{Stack supervision}] Stack manager's does not implement full control loop, as specified by Cloud-SAP. Instead it is solely focused on planning and execution:
\begin{itemize}
 \item planning - Stack manager retrieves problem resolution requests from container manager. It internally maps diagnosed problems to actions as stated in table \ref{tab:stack-manager-planning}. Similarly to a container manager, it attempts to reserve resources needed to implement desired change. In case when it is not possible, it problem is further delegated - to a cloud instance manager.

 \item execution - Manager horizontally scales container invoking OpenNebula frontend API through cloud provider client. Noticeably, currently only adding and removing slave instances is possible. Hence, attempts to re-scale master instance (i.e. load balancer) are not supported.
\end{itemize}

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}{ l  l l l }
\specialrule{.1em}{.05em}{.05em} 
\textbf{Description} & \textbf{Container's symptom} & \textbf{Stack's symptom} & \textbf{Action} \\
\specialrule{.1em}{.05em}{.05em}

Not enough slaves to handle load & \texttt{GREATER\_CPU} (slave) & \texttt{INSUFFICIENT\_SLAVES} &  Add slave \\ \hline
Slaves are not fully occupied & \texttt{LESSER\_CPU} (slave) & \texttt{REDUNDANT} &  Remove slave \\ \hline
Master is overly engaged & \texttt{GREATER\_CPU} (master) & \texttt{OVERLOADED\_MASTER} &  None \\ \hline
Stack is healthy & \texttt{FITS\_CPU} & \texttt{HEALTHY} & None \\ \hline

\end{tabularx}
\caption{Stack manager's symptoms mappings}
\label{tab:stack-manager-planning}
\end{table}

Figure X portrays above-mentioned sequence of steps.

 \item[\textbf{Stack deployment}] Stack deployment is done in two phases:
 \begin{inparaenum}
  \item stacks's resource are reserved apriori
  \item cloud provider client is leveraged to create service's AppFlow template and then instantiating it.
 \end{inparaenum}

\end{asparaenum}

@@

% darek
\subsection{Cloud provider client}
\subsubsection{Objectives}
Cloud provider client is obliged to:

\begin{itemize}
 \item provide a unified access to a subset of cloud provider's features, required from an auto-scaling subsystem perspective
\end{itemize}

\subsubsection{Implementation details}
As for OpenNebula, there are two APIs that have to be supported:
\begin{itemize}
 \item OpenNebula frontend - client is based on OpenNebula's ruby bindings providing access to operations such as virtual machine provisioning, container monitoring. XMLRPC is used as an underlying protocol.
 \item AppFlow - client exposes AppFlow capabilities: creating service template and instantiating it. AppFlow is a REST web service.
\end{itemize}

% darek
\section{Cloud provider}
\subsection{Introduction}
What cloud provider is responsible for is:
\begin{itemize}
 \item deploying, destroying, monitoring virtual machine
 \item deploying, destroying a stack (group of correlated virtual machines)
\end{itemize}

As it was previously mentioned, we selected OpenNebula with AppFlow addition as a cloud provider. Besides, we used OpenVZ as a hypervisor. What is more, we had to supply OpenNebula's computing nodes with an OpenVZ agent - this is to enable vertical scaling, not available by default.

Figure XXX shows exemplary deployment of OpenNebula along with involved components.
